%-------------------------
% Cover Letter in LaTeX
% Author : Gabriel Gomez
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\setlength{\footskip}{5pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.8em}

\pdfgentounicode=1

%-------------------------------------------
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://gabogomez.dev/}{\Large Gabriel Gomez}} & Email: \href{mailto:ggomez.dev@outlook.com}{ggomez.dev@outlook.com} \\
  \href{https://gabogomez.dev/}{gabogomez.dev} & Mobile: \href{tel:+573168325201}{+57-316-832-5201} \\
\end{tabular*}

\vspace{1.2em}

June 13, 2026

\vspace{0.4em}

Sezzle Hiring Team

\vspace{1em}

Dear Sezzle Hiring Team,

I am applying for the Junior Software Engineer role at Sezzle. Two things drew me here equally: a mission I believe in --- making commerce more financially accessible --- and an engineering environment built around scale, automation, and high standards. That combination is exactly what I am looking for.

My background is full-stack with a backend lean. I have built RESTful APIs on Spring Boot and Jakarta EE, worked with relational databases (PostgreSQL, MySQL), and deployed containerized services on Kubernetes running on AWS. On the frontend, I have built SPAs with React and TypeScript --- including MatricuApp, a course enrollment platform with JWT authentication, role-based access control, and a PostgreSQL backend. More recently, I developed a production POS system using NestJS and Electron with an offline-first SQLite architecture, automated unit and integration tests, and full audit trails for inventory reconciliation.

I will be straightforward: I have not written Golang yet. But I learn fast, and I have a habit of proving it in practice rather than on paper. My roots are in Java, so when I took on the POS project I had to adopt NestJS and Electron --- a meaningful paradigm shift from a Java EE backend to an event-driven Node.js runtime with a completely different async model. I found it more interesting than intimidating. Golang's philosophy --- simplicity, explicit error handling, performance --- maps closely to how I already think about building reliable backends. I am confident I will be productive in it quickly, and I am genuinely excited to do it inside a production-scale system.

The fintech angle resonates with me personally. As a freelance contractor for Extreme Technologies I built Afinia PQR, a platform for managing customer complaints and claims for an electric utility. I adapted an existing white-label Android and Jakarta web service system to support a three-role workflow: an administrator creates a case and assigns it to a contractor crew, the contractor submits a field report marking the job resolved or flagged for follow-up, and a supervisor reviews the outcome before closing the case. I implemented the state machine driving case transitions and role-based form routing across mobile app and backend --- a system where traceability is non-negotiable because every PQR carries a regulatory deadline. That experience gave me a strong appreciation for the correctness-under-pressure engineering that financial products demand.

On the AI tools requirement: I use Claude daily --- for research, generating boilerplate, stress-testing logic, and speeding up documentation. I treat it as a multiplier, not a replacement for understanding, and I am comfortable being evaluated on how I use it.

I would welcome the chance to demonstrate what I can contribute to Sezzle.

\vspace{1.5em}

Sincerely,

\vspace{0.4em}

\textbf{Gabriel Gomez}\\
\href{mailto:ggomez.dev@outlook.com}{ggomez.dev@outlook.com}

\end{document}
