%-------------------------
% Resume in LateX
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\setlength{\footskip}{5pt}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://gago852.github.io/}{\Large Gabriel Gomez}} & Email: \href{mailto:ggomez.dev@outlook.com}{ggomez.dev@outlook.com}\\
  \href{https://gago852.github.io/}{gago852.github.io} & Mobile: \href{tel:+573168325201}{+57-316-832-5201} \\
\end{tabular*}





%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Extreme Technologies S.A.}{Barranquilla, CO}
{Software Developer}{Apr 2021 -- Jun 2023}
\resumeItemListStart
\resumeItem{Acuacar Daños}
{Acuacar Daños is a cloud-based crew management system for utility companies, this system is tailored for damage control in the water network and for the water utility company Acuacar. It uses a web page for supervisors, built with Google Web Toolkit (GWT), and an Android app used for contractors to receive tasks, track the progress of the task using geo-location data (GPS) and report back to the system.}
\resumeItem{Promigas}
{Promigas is a cloud-based crew management system for utility companies, this system is tailored for inspections in the gas network and for the company Promigas. It uses a web page for supervisors, built with Google Web Toolkit (GWT), and an Android app used for contractors to receive tasks, track the progress of the task using geo-location data (GPS) and report back to the system, also has a feature to track the route that the contractor takes in real time while he is doing the inspection.}

\resumeItem{Podas y Lavados}
{Podas y Lavados is a cloud-based crew management system for electrical network maintenance, tree pruning and specially designed for Aire and Afinia. It uses a web page for supervisors, built with Google Web Toolkit (GWT), and an Android app used for contractors to receive tasks, track the progress of the task using geo-location data (GPS) and report back to the system. Another feature is granting the contractor the ability to survey the tree that are not in the database, imported from a Keyhole Markup Language file (KMZ) from Google Earth.}

\resumeItem{SEPT Santa Marta}
{SEPT Santa Marta is a cloud-based public bus transportation system for the city of Santa Marta. It uses several technologies including Amazon Lambdas, Digi Routers, and a ticket validator running on Android. Another feature is the integration of the police command and control center to track the buses in real time, the use of a panic button to call the police, and the use of virtual wallets to pay for the bus ticket with QR codes.}

\resumeItemListEnd

% --------Multiple Positions Heading------------
%  \resumeSubSubheading
%   {Software Engineer I}{Oct 2014 -- Sep 2016}
%   \resumeItemListStart
%      \resumeItem{Apache Beam}
%        {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%   \resumeItemListEnd

%-------------------------------------------

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Universidad Autónoma del Caribe}{Barranquilla, CO}
{Bachelor of System Engineering}{Feb 2018 -- May 2023}
\resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Weather App}
{Open-source weather Android app built with Kotlin and Jetpack Compose provides real-time forecasts, location-based updates, and a modern, customizable UI using the OpenWeather API.}
\resumeSubItem{Resume Builder on LateX}
{Open-source résumé generator uses LaTeX to create professional PDFs, leveraging GitHub Actions for automated building and deployment.}
\resumeSubHeadingListEnd


%--------SKILLS------------
\section{Skills}
\resumeSubHeadingListStart
\item{
            \textbf{Languages}{: Java, Kotlin, SQL, TypeScript, JavaScript, HTML, CSS, Dart, Python}
            
      }
\item {
            \textbf{Technologies}{: AWS, Android, React, Astro, Jetpack Compose, Flutter, PostgreSQL, MySQL, Firebase, Git, Docker, Kubernetes, Espresso, Mockito, JUnit, Test-Driven Development, Clean Architecture, SOLID, Design Patterns, RESTful APIs, Microservices, CI/CD, Agile, Scrum, Maven, Gradle, Jira}
      }
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
