%-------------------------
% Resume in LateX
% Author : Gabriel Gomez
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\setlength{\footskip}{5pt}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://gabogomez.dev/}{\Large Gabriel Gomez}} & Email: \href{mailto:ggomez.dev@outlook.com}{ggomez.dev@outlook.com}\\
  \href{https://gabogomez.dev/}{gabogomez.dev} & Mobile: \href{tel:+573168325201}{+57-316-832-5201} \\
\end{tabular*}




%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Self-employed}{Barranquilla, CO}
{Freelance Software Developer}{Jun 2025 -- Present}
\resumeItemListStart
\resumeItem{Web Service Migration}
{Migrated a Java EE web service to Spring Boot, redesigning RESTful APIs consumed by an Android client, and deployed on Kubernetes on AWS. Built a Makefile-driven dev environment spinning up Docker Compose with a PostgreSQL test database, building images, and injecting environment variables.}
\resumeItem{POS System}
{Built a desktop POS system with Electron and NestJS (TypeScript), featuring offline-first SQLite storage, USB printing, barcode scanner support, and inventory management with full audit trails. Wrote unit and integration tests to validate stock reconciliation and transaction processing logic.}
\resumeItemListEnd

\resumeSubheading
{Extreme Technologies S.A.}{Barranquilla, CO}
{Software Developer}{Apr 2021 -- Jun 2024}
\resumeItemListStart
\resumeItem{Acuacar Daños}
{Maintained and developed features across the Android app and Jakarta EE RESTful web service of a cloud-based crew management system. Migrated the app to Android 11 and implemented a multi-step workflow spanning mobile client and backend, coordinating data consistency between layers.}
\resumeItem{Promigas}
{Adapted a white-label crew management system for a gas utility client. Implemented real-time GPS tracking, integrated PostGIS for geographic data processing in PostgreSQL, and optimized the backend API to handle concurrent real-time sessions at scale.}
\resumeItem{SETP Santa Marta}
{Implemented a middleware layer in an Android fare validator for a public bus system. Built payment validation for physical cards and QR codes, and designed an offline-first transaction queue that syncs to the backend on reconnection, ensuring zero data loss under intermittent connectivity.}

\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Universidad Autónoma del Caribe}{Barranquilla, CO}
{Bachelor of System Engineering}{Feb 2018 -- May 2023}
\resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{MatricuApp}
{Course enrollment SPA with React (TypeScript) frontend and Spring Boot backend, using JPA, JWT via Spring Security, and a Neon PostgreSQL database. Features role-based access control, credit-limit enforcement, and a RESTful API.}
\resumeSubItem{Personal Portfolio}
{Web application built with Astro and Tailwind CSS, deployed on Cloudflare with Edge Functions for automatic browser-language redirection and a multilingual experience.}
\resumeSubItem{Resume Builder on LateX}
{Open source resume generator using LaTeX with GitHub Actions for automated PDF building and versioned GitHub Releases via CI/CD.}
\resumeSubHeadingListEnd

%-----------Courses and Certifications-----------------
\section{Courses and Certifications}
\resumeSubHeadingListStart
\resumeSubItem{Udemy - React: From Zero to Expert}{Mar 2026}
\resumeSubItem{Platzi - AI Tools for Developers}{Apr 2025}
\resumeSubItem{Udemy - Android Testing Course with JUnit, Mockito, Espresso and TDD}{Feb 2024}
\resumeSubItem{Platzi - Git and GitHub Professional Course}{Sep 2019}
\resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
\resumeSubHeadingListStart
\item{
            \textbf{Languages}{: TypeScript, JavaScript, SQL, Java, Kotlin, Python, Dart, HTML, CSS, LaTeX}
      }
\item {
            \textbf{Technologies}{: React, React Native, NestJS, Spring Boot, RESTful APIs, AWS, Kubernetes, Docker, Docker Compose, PostgreSQL, MySQL, SQLite, Firebase, Git, GitHub Actions, Gitlab CI/CD, Electron, Astro, Tailwind CSS, Jetpack Compose, Flutter, Espresso, Mockito, JUnit, Test-Driven Development, Clean Architecture, SOLID, Design Patterns, Microservices, Agile, Scrum, Maven, Gradle, Make, Jira}
      }
\item {
            \textbf{AI Tools}{: Claude (daily use for productivity, research, and code generation), GitHub Copilot}
      }
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
