%-------------------------
% Resume in LateX
% Author : Gabriel Gomez
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\setlength{\footskip}{5pt}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://gabogomez.dev/}{\Large Gabriel Gomez}} & Email: \href{mailto:ggomez.dev@outlook.com}{ggomez.dev@outlook.com}\\
  \href{https://gabogomez.dev/}{gabogomez.dev} & Mobile: \href{tel:+573168325201}{+57-316-832-5201} \\
\end{tabular*}





%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Self-employed}{Barranquilla, CO}
{Freelance Software Developer}{Jun 2025 -- Present}
\resumeItemListStart
\resumeItem{Web Service Migration}
{Migrated a web service from Java EE to Spring Boot and implemented Kubernetes for container orchestration. Built an automated development environment using a Makefile to streamline workflows including spinning up a Docker Compose stack with a test database, building container images, running the project with environment variables, and initializing configuration files.}
\resumeItemListEnd

\resumeSubheading
{Extreme Technologies S.A.}{Barranquilla, CO}
{Software Developer}{Apr 2021 -- Jun 2024}
\resumeItemListStart
\resumeItem{Acuacar Daños}
{Maintained and developed features for the Android app and Jakarta web service of a cloud-based crew management system for water utility Acuacar. Redesigned the complete UI for a modern interface, migrated the app to support Android 11, and implemented a workflow modification spanning both the mobile app and the web service.}
\resumeItem{Promigas}
{Adapted a white-label crew management system for a new gas utility client, developing the Android app and Jakarta web service. Implemented real-time GPS tracking to map contractor routes during pipeline inspections, integrated PostGIS for geographic coordinate processing, and optimized the web service to handle the increased load from concurrent real-time sessions.}
\resumeItem{Podas y Lavados}
{Adapted a white-label system for power grid maintenance and tree trimming serving Aire and Afinia. Built a multi-role Android app supporting two parallel workflows and implemented a GIS feature that downloads and renders map layers with tree and power pole positions and statuses from the web service.}
\resumeItem{SETP Santa Marta}
{Implemented a middleware layer in an Android-based fare validator for a public bus transportation system. Built payment validation for physical cards and QR codes from virtual wallets, and designed an offline-first queue to store transactions during connectivity loss and sync them when the connection is restored.}

\resumeItemListEnd

% --------Multiple Positions Heading------------
%  \resumeSubSubheading
%   {Software Engineer I}{Oct 2014 -- Sep 2016}
%   \resumeItemListStart
%      \resumeItem{Apache Beam}
%        {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%   \resumeItemListEnd

%-------------------------------------------

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Universidad Autónoma del Caribe}{Barranquilla, CO}
{Bachelor of System Engineering}{Feb 2018 -- May 2023}
\resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Weather App}
{Open-source weather app for Android built with Kotlin and Jetpack Compose that provides real-time forecasts, location-based updates, and a modern, customizable UI using the OpenWeather API.}
\resumeSubItem{Resume Builder on LateX}
{Open source resume generator that uses LaTeX to create professional-looking PDFs, and utilizes GitHub Actions for automated building and deployment.}
\resumeSubItem{Personal Portfolio}
{Personal web portfolio built with Astro and Tailwind CSS, deployed on Cloudflare. Implements Cloudflare's Edge Functions for automatic redirection based on browser language, offering an optimized, high-performance multilingual experience.}
\resumeSubItem{MatricuApp}
{Technical test solution — a university course enrollment webapp where students can log in, enroll in and drop courses for their current semester, with credit limits enforced per semester. Built the frontend with React and the backend with Spring Boot, Maven, JPA, JWT authentication via Spring Security, and a Neon PostgreSQL database.}
\resumeSubHeadingListEnd

%-----------Courses and Certifications-----------------
\section{Courses and Certifications}
\resumeSubHeadingListStart
\resumeSubItem{Universidad autónoma del caribe - New Engineering Trends}{Feb 2023}
\resumeSubItem{Udemy - Jetpack Compose from scratch, migrate your Android XML views}{Apr 2024}
\resumeSubItem{Udemy - Android Testing Course with JUnit, Mockito, Espresso and TDD}{Feb 2024}
\resumeSubItem{Platzi - Git and GitHub Professional Course}{Sep 2019}
\resumeSubItem{Udemy - React: From Zero to Expert}{Mar 2026}
\resumeSubItem{Platzi - AI Tools for Developers}{Apr 2025}
\resumeSubItem{Platzi - Android UI Design with Android Studio}{Jul 2020}
\resumeSubItem{Platzi - Flutter Course}{Mar 2021}
\resumeSubItem{Platzi - Advanced Flutter Course}{Apr 2022}
\resumeSubItem{Platzi - Introduction to Java SE}{Oct 2020}
\resumeSubItem{Platzi - Object-Oriented Java SE}{Feb 2021}
\resumeSubItem{Platzi - Basic Kotlin Course}{Oct 2019}
\resumeSubItem{Platzi - Kotlin for Android Course}{May 2020}
\resumeSubItem{Platzi - Terminal and Command Line Introduction Course}{Apr 2020}
\resumeSubItem{Platzi - Android Technical Basics Course}{Nov 2019}
\resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
\resumeSubHeadingListStart
\item{
            \textbf{Languages}{: Java, Kotlin, SQL, TypeScript, JavaScript, HTML, CSS, Dart, Python, LaTeX}

      }
\item {
            \textbf{Technologies}{: AWS, Android, Astro, React, Tailwind CSS, Cloudflare Edge Functions, Google Web Toolkit (GWT), Jetpack Compose, Flutter, Spring Boot, Kubernetes, Docker, Docker Compose, PostgreSQL, MySQL, Firebase, Git, GitHub Actions, Espresso, Mockito, JUnit, Test-Driven Development, Clean Architecture, SOLID, Design Patterns, RESTful APIs, Microservices, CI/CD, Agile, Scrum, Maven, Gradle, Make, Jira}
      }
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
